Energy and the CES production function

### 2015-08-21 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
tweak triplot and add sigma plot

@@

@@

<<fig.height=3>>=
triPlot(
  data=
    AllCoeffs %>% 
    mutate( Model = interaction(nest, CSP, sep = " -- ", drop=TRUE),
            Inputs = flavor), 
  labels = c("alpha[k]", "alpha[l]", "alpha[e]"),
  aes(x = alpha_1, y = alpha_2, z = alpha_3, 
      fill  = Model, 
      shape = Model,
      size = Model, 
      color = Inputs),
  alpha = 0.6) +
  facet_grid(. ~ Country) +
  scale_colour_manual(values = c("gray70", "black")) +
  scale_size_manual(values = c(5, 3,3,3,3)) +
  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6)) +
  scale_shape_manual(values = 21:25) +
  guides( 
    col = guide_legend(override.aes = aes(size = 5, shape = 21)) )
@

>>>>

AllCoeffs <-
  AllCoeffs %>% 
  mutate( 
    nest = ifelse(is.na(nest), "", nest)
    )

@@

<<>>=
ggplot(
  AllCoeffs %>% 
    gather(type, value, matches("sigma")) %>% 
    filter(!is.na(value)) %>% 
    filter(! type %in% c("sigma", "sigma_1")) %>%
    mutate( Model = interaction(nest, CSP, sep = " ", drop=TRUE),
            Inputs = flavor) 
  ) + 
  geom_point(aes(x=.0001 + value, y=type, 
                 shape = Model, fill=Model, size=Model,
                 color=Inputs
                 )
                 #position = position_jitter(height=0.2, width=0)
             ) + 
  facet_grid( type ~ Country, scales = "free_y" ) + 
  scale_x_log10(limits = c(0.001,2000)) +
  xy_theme() +
  scale_colour_manual(values = c("gray70", "black")) +
  scale_size_manual(values = c(5, 3,3,3,3,3,3)) +
  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6, .6, .6)) +
  scale_fill_manual(values = c(scales::alpha("gray50", .2), rep("transparent", 6))) +
  scale_shape_manual(values = c(21, 21, 23:27)) +
  guides( 
    col = guide_legend(override.aes = aes(size = 5, shape = 21))
    )

@

@@

<<fig.height=3>>=
triPlot(
  data=
    AllCoeffs %>% filter(model == "CES") %>%
    mutate( Model = interaction(nest, CSP, sep = " ", drop=TRUE),
            Inputs = flavor), 
  grid_lines = 5,
  labels = c("alpha[k]", "alpha[l]", "alpha[e]"),
  aes(x = alpha_1, y = alpha_2, z = alpha_3, 
      fill  = Model, 
      shape = Model,
      size = Model,
      color = Inputs)
  ) +
  facet_grid(. ~ Country) +
  scale_colour_manual(values = c("gray70", "black")) +
  scale_size_manual(values = c(5, 3,3,3,3,3,3)) +
  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6, .6, .6)) +
  scale_fill_manual(values = c(scales::alpha("gray50", .2), rep("transparent", 6))) +
  scale_shape_manual(values = c(21, 21, 23:27)) +
  guides( 
    col = guide_legend(override.aes = aes(size = 5, shape = 21)) )
@
